An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-05-03 Article/EconGrowth2.Rnw
Changed country and energy levels on all scatter plots.

<<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
cesCoeffsData <- loadResampledData(archive=archive, 
                                   country=countryAbbrevs, 
                                   model="ces", 
                                   factors=c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"), 
                                   kind="coeffs")
standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStr, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

@@

\twocolumn{}
<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
linexCoeffsData <- loadResampledData(archive=archive, 
                                     country=countryAbbrevs, 
                                     model="linex", 
                                     factors=c("iK+iL+iQ"), 
                                     kind="coeffs")

>>>>

<<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
cesCoeffsData <- loadResampledData(archive=archive, 
                                   country=countryAbbrevs, 
                                   model="ces", 
                                   factors=c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"), 
                                   kind="coeffs")
# Rearrange the country factors to obtain our preferred ordering.
cesCoeffsData$country <- as.factor(cesCoeffsData$country)
for (lev in rev(countryAbbrevs)) { cesCoeffsData$country <- relevel(cesCoeffsData$country, ref=lev) }
standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStr, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

@@

\twocolumn{}
<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
linexCoeffsData <- loadResampledData(archive=archive, 
                                     country=countryAbbrevs, 
                                     model="linex", 
                                     factors=c("iK+iL+iQ"), 
                                     kind="coeffs")
# Rearrange the country factors to obtain our preferred ordering.
linexCoeffsData$country <- as.factor(linexCoeffsData$country)
for (lev in rev(countryAbbrevs)) { linexCoeffsData$country <- relevel(linexCoeffsData$country, ref=lev) }
